SDR enhancement by clouds

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 12:17
Commit 2024-03-07 13:13

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid)
- any day without clouds and EC events
- 20 days with at least 60% of day length without clouds and some EC events
- 30 random days
- some manual selected days that were included during the manual inspection

@@

>>>>

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid) @Natsis2023
- any day without clouds and EC events
- 20 days with at least 60% of day length without clouds and some EC events
- 30 random days
- some manual selected days that were included during the manual inspection

@@

### Yearly plots relative to all GHI data.

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-1.png")
```

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-2.png")
```

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-3.png")
```
